CannonRV: Measuring radial velocities with a data-driven spectral model

### 2017-02-28 paper/ms.tex
Fit labels and abc simultaneously

@@

Working on it...

@@

>>>>

%% Let's do it in a simple way

@@

Suppose we have a trained Cannon model. To infer the labels from the fluxes, we need to minimize the objective function:

\begin{equation}
l_m \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n}-V(l_m)\cdot \theta_j)^2} \over {e^2_{j,n}}} \right]
\end{equation}

$l_m$ is the $m$ th label of star n. V is the vectorizer and ${e^2_{j,n}}$ is the error of star n at pixel j, which include scatter and variance.

If we include parameters a, b and c, the objective function will be:

\begin{equation}
l_m, a, b, c \leftarrow \left[ \sum_{j=1}^{j=J}{({y_{j,n} - a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1})^2} \over {e^2_{j,n}}} \right]
\end{equation}

Now we can obtain inferred labels and a, b and c simultaneously. And the new inferred flux is:

\begin{equation}
y_{j,n}^{inf,sim} = a*V(l_m)\cdot \theta_{j + 1} - b*V(l_m)\cdot \theta_{j} - c*V(l_m)\cdot \theta_{j-1}
\end{equation}

$y_{j,n}^{inf,sim} $ is the inferred flux from the new method, which fits labels and abc simultaneously.

The results from this method are in experiment 5

@@

 \subsection{\label{sec:level2}Experiment 5}
 In experiment 5, we will check whether our method works. The method is to plot the new inferred labels against reference labels. Here we use the 548 stars in the training set.

 \begin{center}
\includegraphics[width=170mm]{sim_diagnostic.png}

\centerline{Fig.15 Inferred labels VS reference labels of the new method.}

From figure 15 we can see that the inferred labels are close to the reference labels, which means the method works.

 After that, we show the histogram of parameters a, b and c.

 \begin{center}
\includegraphics[width=170mm]{hist_rv_abc_sim.png}

\centerline{Fig.16 The histogram of the results from simultaneous fitting}

We also shows the results VS FiberID, RA, DEC, SNR, HJD and AirMass.

 \begin{center}
\includegraphics[width=170mm]{ve_vs_all_sim.png}

\centerline{Fig.17 RV shifts from simultaneous fitting}

# We also compare the results from the whole spectrum(The original method) and fitting simultaneously.

 \begin{center}
\includegraphics[width=170mm]{old_vs_new_sim.png}

\centerline{Fig.18 Comparison of the results from fitting the whole spectrum and fitting simultaneously}
